---
title: "Medfly Research"
author: "Camden Possinger"
output: 
      prettydoc::html_pretty:
        theme: hpstr
        highlight: github
---
```{r Data Prep, include=FALSE}
library(plotly)
library(survminer)
library(readr)
library(magrittr)
library(dplyr)
library(ggplot2)
library(survival)
library(generics)
library(broom)

# : Load Data ####
male <- read_delim("/home/cam/Documents/Reseach Fall 2020/Data/MALE.txt",delim = "    ")
female <- read_delim("/home/cam/Documents/Reseach Fall 2020/Data/FEMALE.txt",delim = "    ")

# : Data Prep ####

age <- c(1:173)
total_female <- female %>% slice(3718:n()) %>% select(`      Cohort`)
total_female$`      Cohort` %<>% as.numeric 
total_male <- male %>% slice(3718:n()) %>% select(`      Cohort`)
total_male$`      Cohort` %<>% as.numeric 
female_male_total <- tibble("Age" = age,"Female" = total_female$`      Cohort`,
                            "Male" = total_male$`      Cohort`) 


female_surv_data_prep <- function(vec,vec_age){
  num_died <- c()
  num_died_final <- c()
  new_age <- c()
  final_vec <- c()
  for(i in vec){
    if(i == vec[1]){
      num_died %<>% append(0) 
    }
    else{
      total_minus_item <- (605528)- i
      num_died %<>% append(total_minus_item)
      
    }
  }
  for(k in vec_age){
    if(k == 1){
      num_died_final %<>% append(0) 
    }
    else{
      num_died_final %<>% append(num_died[k]-num_died[k-1])  
    }
    
  }
  
  for(j in vec_age){
    new_age %<>% append(c(rep(j ,num_died_final[j]))) 
  }
  for(l in vec_age){
    final_vec %<>% append(c(rep(1,num_died_final[l]))) 
  }
  final_data <- data.frame("Age" = new_age,"Dead Female Flies" = final_vec)
  return(final_data)
}


female_surv_data <- female_surv_data_prep(female_male_total$Female %>% as.integer,age)

male_surv_data_prep <- function(vec,vec_age){
  num_died <- c()
  num_died_final <- c()
  new_age <- c()
  final_vec <- c()
  for(i in vec){
    if(i == vec[1]){
      num_died %<>% append(0) 
    }
    else{
      total_minus_item <- (598118)- i
      num_died %<>% append(total_minus_item)
      
    }
  }
  for(k in vec_age){
    if(k == 1){
      num_died_final %<>% append(0) 
    }
    else{
      num_died_final %<>% append(num_died[k]-num_died[k-1])  
    }
    
  }
  for(j in vec_age){
    new_age %<>% append(c(rep(j ,num_died_final[j]))) 
  }
  for(l in vec_age){
    final_vec %<>% append(c(rep(1,num_died_final[l]))) 
  }
  final_data <- data.frame("Age" = new_age,"Dead Male Flies" = final_vec)
  return(final_data)
}
male_surv_data <- male_surv_data_prep(female_male_total$Male %>% as.integer,age)
```

### Probability Density Function
When we look at two samples and their PDF's we can see for what values the sample are the same and what are different



Male Density Estimation
```{r echo=FALSE}
male_density <- total_male$`      Cohort` %>% as.vector %>% density
male_density
```
Female Density Estimation
```{r echo=FALSE}
female_density <- total_female$`      Cohort` %>% as.vector %>% density
female_density
```
```{r echo=FALSE}
total_histogram <- ggplot(data = female_male_total)+geom_histogram(aes(x = Female,y = ..density..),bins = 50,fill = "lightblue") + geom_histogram(data = female_male_total,aes(x = Male,y = ..density..),bins = 50,fill = "pink") + xlab("Male: Light Blue      Female: Pink")

total_histogram %<>% ggplotly
total_histogram

density_plot <-ggplot(data = female_male_total,aes(x = Female))+
  geom_density(color = "pink",show.legend = FALSE)+ 
  geom_density(data = female_male_total,aes(x = Male),color = "lightblue",show.legend = FALSE)+
  xlab("Male: Light Blue      Female: Pink")

density_plot %<>% ggplotly
density_plot
```

### Cumulative Distribution Function

We can use the estimated Cumulative Distribution Function to calcualte the cumulative probability for a given x-value and determine if the probability that a data value is less than or equal to a certain value.

```{r echo=FALSE}
female_cdf <- ecdf(female_male_total$Female)
female_cdf(0.0)
male_cdf <- ecdf(female_male_total$Male)
male_cdf(0.0)
```
```{r echo=FALSE}
cdf_plot <- ggplot(female_male_total) + 
  stat_ecdf(aes(x = Female),geom = "step",pad = FALSE,color = "pink")+
  stat_ecdf(aes(x = Male),geom = "step",pad = FALSE,color = "lightblue")+
  xlab("Male: Light Blue      Female: Pink")
cdf_plot %<>% ggplotly
cdf_plot
```

### Survival Function

The probability that a fly will survive beyond any specified time.

```{r echo=FALSE, message=FALSE, warning=FALSE}
female_surv <- survfit(Surv(female_surv_data$Age,female_surv_data$Dead.Female.Flies)~1,data = female_surv_data)
male_surv <- survfit(Surv(male_surv_data$Age,male_surv_data$Dead.Male.Flies)~1,data = male_surv_data)
fit <- list("Male"=male_surv,"Female"=female_surv)

surv_plot <- ggsurvplot(
  fit = fit,
  combine = TRUE,
  conf.int = TRUE,
  conf.int.style = "step",
  risk.table = TRUE,
  tables.theme = theme_cleantable(),
  palette = c("lightblue","pink"),
  xlab = "Days",
  ylab = "Overall Survival Probability"
)
surv_plot$plot %>% ggplotly
```



